---
title: "mod2 - R markdown doc 1"
author: "Sia Gerard"
date: "2025-04-21"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a level 1 header

### This is a level 3 header

Here is a link to [GOOGLE](https://www.google.com/)

Here is a word in **bold** and another word in __bold__.

Here is a word in *italics* and another word in _italics_.

When we compile our document, we are using the `rmarkdown` package.

Here are some example R commands:

```
2+2
mean(c(1,2,3,4,5))
```


Here is an example of a non-numbered list:

* Breakfast
    - food
        + eggs
        + toast
        + bacon
    - drink
        + apple juice
* Lunch
    - taco
* Dinner
    - baked chicken
    - broccoli
    - rice


Here is an example of a numbered list:

1. Breakfast
    a. food
        i. eggs
        ii. toast
        iii. bacon
    b. drink
        i. apple juice
2. Lunch
    a. taco
3. Dinner
    a. baked chicken
    b. broccoli
    c. rice


Here is an example of a blockquote:

> This is a block quote. This
> paragraph has two lines.
>
> 1. This is a list inside a block quote.
> 2. Second item.


Here is an example of a nested blockquote:

> This is a block quote. This
> paragraph has two lines.
>
> > This text is nested


Here is an example of code in a blockquote:

>     2+2
>     mean(c(1,2,3,4,5))


_________________________________________

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r pressure 2, echo=TRUE, fig.height=5, fig.width=5}
plot(pressure)
```

## Insert Tables
```{r}
knitr::kable(head(cars),
             caption = "top six rows of cars dataset"
             )
```

##insert and equation with laTec
$$ Y= \beta_0 + \beta1x $$

